---
title: "Bechdel Solution"
author: "Niklas Cypris"
date: "1 4 2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(visdat)
library(car)
library(ggResidpanel)
library(parameters)

Sys.setenv(LANG = "en")
```

# Tasks

Filter movies from 1990
Visualize missing cases
Compute fail-pass from clean_test
Compute gross overall income of movie - select 2013 levels
Center Predictors
Visualize distributions of predictors
Visualize distributions of pass-fail by year
Check assumptions of multiple regression
conduct multiple regression or bootstrapping:
gross ~ test + budget + metascore + imdb_rating
write an answer to the research question

# READ CSV

```{r}
df <- read_csv(file = "./data/bechdel.csv")
```

# Filter >= 1990

```{r}
df <- df %>% 
  filter(year >= 1990)
```

# Visualize Missing

```{r}
df %>% 
  vis_miss()
```

# Compute Pass - Fail

Look at values

```{r}
table(df$clean_test)
```

Create variable

```{r}
df <- df %>% 
  mutate(pass_fail = ifelse(df$clean_test == "ok", 1, 0)) # pass == 1
```

Make sure everything went well

```{r}
df %>% 
  select(clean_test, pass_fail) %>% 
  head(10)
```

# Compute gross overall income of movie

```{r}
df <- df %>% 
  mutate(gross_2013 = domgross_2013 + intgross_2013,
         gross = domgross + intgross)
```

Make sure everything went well

```{r}
df %>% 
  select(gross_2013, domgross_2013, intgross_2013, gross, domgross, intgross) %>% 
  head(10)
```

# Center Predictors

```{r}
df <- df %>% 
  mutate(budget_c = scale(budget, scale = FALSE)[,1],
         budget_2013_c = scale(budget_2013, scale = FALSE)[,1],
         metascore_c = scale(metascore, scale = FALSE)[,1],
         imdb_rating_c = scale(imdb_rating, scale = FALSE)[,1]
         )
```

Make sure everything went well

```{r}
df %>% 
  select(budget_c, budget, budget_2013_c, budget_2013, metascore_c, metascore, imdb_rating_c, imdb_rating) %>% 
  head(10)
```

# Visualize Distributions of Predictors

## Budget

```{r}
ggplot(df, aes(x = budget)) +
  geom_histogram(bins = 100)
```

## Budget 2013

```{r}
ggplot(df, aes(x = budget_2013)) +
  geom_histogram(bins = 100)
```

## Metascore

```{r}
ggplot(df, aes(x = metascore)) +
  geom_histogram(bins = 70)
```

## IMDB Rating

```{r}
ggplot(df, aes(x = imdb_rating)) +
  geom_histogram(bins = 70)
```

# Pass-Fail by Year

## Absolute

```{r}
df %>% 
  mutate(pass_fail = as.factor(pass_fail)) %>% 
  ggplot(aes(x = year, fill = pass_fail)) +
  geom_bar() +
  theme_classic()
```

## Proportional

```{r}
df %>% 
  mutate(pass_fail = as.factor(pass_fail)) %>% 
  ggplot(aes(x = year, fill = pass_fail)) +
  geom_bar(position = "fill") +
  theme_classic()
```

# Multiple Regression

```{r}
lm <- lm(gross_2013 ~ pass_fail * budget_2013_c * metascore_c * imdb_rating_c, df)
```

```{r}
summary(lm)
```

# Assumptions

* Variable scales

* Independent observations

* Collinearity

Any violation of the following assumptions reduces the validity of the significance test:

* Normally distributed errors

* Independent errors

* Homogeneous error variance (homoscedasticity)

## Variable scales

Predictors: interval or categorical

Criterion: interval

## Independent observations

E.g. not multiple observations of one person

## Collinearity

Limited correlation between predictors desirable.


Collinearity

* increases standard errors (thus reducing power)

* makes interpretation of results harder


**Variance Inflation Factor (VIF)**

Square root of the variance inflation factor: Standard error increase compared to if the variable had 0 correlation to other predictor variables in the model. 

Rule of thumb 1: No VIF greater than 10

```{r}
vif(lm)
```

Rule of thumb 2: Average VIF not substantially greater than 1

```{r}
mean(vif(lm))
```

### Violation

Remove a predictor

Combine predictors

### IMDB and Metascore grouped

```{r}
df %>% 
  select(imdb_rating, metascore, budget, pass_fail) %>% 
  drop_na() %>% 
  cor()
```

```{r}
df %>% 
  select(imdb_rating, metascore, budget, pass_fail) %>% 
  drop_na() %>% 
  plot() # Thanks, Yi Yen :)
```


```{r}
df <- df %>% 
  mutate(imdb_rating_z = scale(imdb_rating)[,1],
         metascore_z = scale(metascore)[,1],
         acclaim = imdb_rating_z + metascore_z)
```

```{r}
lm2 <- lm(gross_2013 ~ pass_fail * budget_2013_c * acclaim, df)
```

```{r}
summary(lm)
```

```{r}
summary(lm2)
```

```{r}
vif(lm2)
```

```{r}
mean(vif(lm2))
```


## Normally distributed errors

```{r}
plot(lm2)
```

## Independent errors

Test for autocorrelation (e.g. errors are correlated with each other). If autocorrelation is present, you can predict residuals for some observations based on the residuals of other observations.

**Durbin-Watson Test**

P-values not significant = independent errors

```{r}
dwt(lm2)
```

## Homoscedasticity

Variance of the residuals constant across all values.

```{r}
resid_panel(lm2, plots = c("resid", "ls"), smoother = TRUE)
```

```{r}
resid_xpanel(lm2, smoother = TRUE)
```

### Violation

Switch to non-parametric tests

# Results fro multiple regression and bootstrapping

```{r}
summary(lm2)
```

```{r}
set.seed(161)
bootstrap_parameters(lm2, iterations = 5000)
```

# Result

RQ1: Does passing the Bechdel test predict its overall box office success?

YES (yay feminism)

RQ2: Does critical acclaim predict overall box office success?

YES

RQ3: Does the budget predict overall box office success?

YES

RQ4: Does overall box office success depend on any interactions?

Yes for: budget_2013_c:acclaim


