---
title: "session7_dataviz_codealong"
output: pdf_document
---

```{r setup}
library(tidyverse)
library(patchwork)
library(ggcorrplot)
library(psych)
library(visdat)

Sys.setenv(LANG = "en")
```


# QUICK REVIEW

Load in the dataset
```{r}
majors <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-10-16/recent-grads.csv")
```

Let's have a look at our dataset
```{r}
View(majors)
```

Visualize any missing data
```{r}
majors %>% 
  vis_miss()
```

For some reason all the Major names are in all caps, which is not necessarily a problem, just annoying.
Cool R trick though, we can change that!
```{r}
majors <- majors %>% 
  mutate(Major = str_to_title(Major))
```


```{r}
head(majors)
```

## Let's review a couple of the more common graphs

## ONE CATEGORICAL VARIABLE

### 
Make a plot of how many majors are in each of the various major categories:
```{r}

```


## ONE CONTINUOUS VARIABLE

###
Visualize the distribution of the unemployment rate (this was calculated as # of unemployed/Total #)
```{r}

```


## TWO CONTINUOUS VARIABLES

### 
Plot the relationship between median salary and unemployment rate
```{r}

```
## CONTINUOUS WITH CATEGORICAL

### 
Visualize the distribution of the median salary for each major category
```{r}

```

-----------------------------
# CUSTOMIZING OUR PLOTS


## FLIPPING AND REORDERING

Let's go back to the boxplot above. How could we make this more understandable?

```{r}
  
```

Let's look at another example of this where we look at the median salary for each major within the Engineering category. 

```{r}

```


```{r}

```

#EXERCISE

Pick a major category. Make a flipped, ordered barplot of the share of women for each major in that category. Which major from that category has the highest share of women? Which one has the least?

```{r}

```



# Adding text to our data inside of plots


We can use geom_text() or geom_label() to automatically label data in our graph. This is most typically used in scatterplots.

Scatterplot of the the unemployment rates and median salary for each education major using geom_text()
```{r}

```

We can also color the labels.
```{r}
  
```

We can use geom_label to do the same thing with a slightly different look. 
```{r}

```

We can also add our own custom labels and text anywhere in the plot

```{r}
           
```


# EXERCISE
Use geom_label() to add a label next to the highest point on the scatter plot (Median vs unemployment rate) you made in the previous example.

```{r}

```


## Editing plot labels and titles

There are a couple different ways to do this in ggplot. As we know from last semester, we can use the "ggtitle" command to add an overall title to our plot:


```{r}
 
```

We can also use xlab() or ylab() to adjust the labels for the respective axes:

```{r}

```


We can also adjust the labels in the scale function as well with the "name = " argument:

```{r}

```


However, we can also use the labs() function, which allows us to add a title, subtitle, x label, y label and caption all in one function:

```{r}

```


# EXERCISE

## Make a scatterplot visualizing the relationship between amount of people with non college degree jobs and amount of people with low wage jobs. Use the labs() function to label the axes, add a title and a subtitle. 
```{r}


```

## Multiple Plots

## Using Facets

Last semester you learned how to use the two facet functions in ggplot to get multiple graphs in one grid. Let's review this really quickly.

```{r}
ggplot(majors, aes(x = ShareWomen))+
  geom_density()+
  facet_wrap(.~Major_category)
```

However, what if we want to combine different types of graphs that don't have a common variable? (E.g., a scatterplot, barchart and histogram)

We can use the "patchwork" package for this:
```{r}

```

And we save it using ggsave()
```{r}

```



#EXERCISE
## Make a histogram of Median Salary, a barplot of Median salary within the Health majors and one other graph of your choice. Combine them into one figure and save it.

```{r}

```

# INSPECTING DATA & VISUALIZING CORRELATIONS

## Check multiple histograms
```{r}

```

# Pairs plot
```{r}

```

```{r}

```

# Visualizing correlations using ggcorrplot

There are a lot of different ways to visualize correlation matrices. I like this one. 

First we need to create our correlation matrix. We can do this using by simply using the cor() function:

```{r}
corrmat <- cor(mtcars)
corrmat
```

Now let's make this into a more visual matrix
```{r}
ggcorrplot(corrmat)

```

```{r}

```

We can also include the significance levels (but first we need to make the p value matrix)
```{r}

```

You can then set the function to leave the insignificant correlations blank:
```{r}

```


# EXERCISE

Go back to the data we used for the Bechdel test project. Create a visual correlation matrix like the one above of the budget, domgross, intgross, metascore & imdb rating (and the 2013 variables as well if you want!) 

```{r}

```

----------------------------

I think you guys have already seen this, but I am putting it here again just in case:

https://www.r-graph-gallery.com/



