---
title: "Final Session"
author: "Niklas Cypris"
date: "13 7 2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(psych)

Sys.setenv(LANG = "en")
```

```{r}
df <- read_csv("./data/bechdel.csv")
```


# FUNCTIONS in R

Looking inside a function


## Writing a function

### Example Problem

Centering variables


### Function Elements

```{r}
cen <- function(x){
  
  scale(x, scale = FALSE)[,1]
  
}
```

function(x)

All relevant data/arguments/etc that you want to be able to vary should be defined in the round brackets.

{}

The stuff that the function is supposed to do has to be put in the curly brackets.


Explain the function



# EXERCISES

Write a function called z_standard similar to cen that only gives out the z standardized number vector.

```{r}

```

Write a function that squares each observation you input.

```{r}

```

# FACTOR ANALYSIS

```{r}
load("./data/tum_id.Rda")
```

```{r}
View(tum_id)
```

Number of factors: Visual Inspection


# EXERCISE

Vary the number of factors to one.


Change the cut to .3
