---
title: "Repetition Winter Semester"
author: "Niklas Cypris"
date: "9 4 2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(visdat)

Sys.setenv(LANG = "en")
```

# READ DATA

https://github.com/rfordatascience/tidytuesday/tree/master/data/2018/2018-10-23

```{r}
df <- read_csv(file = "./data/movies.csv")
```

# LOOK AT DATA

```{r}
head(df)
```

```{r eval = FALSE}
View(df)
```

```{r}
df %>% 
  vis_miss()
```

# DATA WRANGLING

* filter()

* select()

* mutate()

* summarize()

## FILTER

Used to choose rows

### REMOVING ALL MOVIES FROM UNIVERSAL

```{r}
unique(df$distributor)
```

```{r}
df_no_uni <- df %>% 
  filter(distributor != "Universal")
```

### EXERCISE

Remove all movies that were released before 2000

## SELECT

Used to choose columns

### PUTTING MOVIE NAME TO THE FRONT

```{r}
df <- df %>% 
  select(movie, everything())
```

```{r}
head(df)
```

### EXERCISE 

Remove the distributor column

## MUTATE

Creating new columns and changing existing ones

### COMPUTE DOMESTIC RETURNS PER DOLLAR INVESTED

```{r}
df <- df %>% 
  mutate(dom_return = domestic_gross/production_budget)
```

```{r}
head(df)
```

### EXERCISE

1. Compute overall box office return per Dollar invested.


2. Compute a column called 'success' that depicts if the overall return of a movie was above 1 (success = TRUE) or if it was equal or below 1 (success = FALSE)

## SUMMARIZE

Collapsing columns to single values

```{r}
df %>% 
  summarise(av_prod_bud = mean(production_budget, na.rm = TRUE),
            median_prod_bud = format(median(production_budget, na.rm = TRUE), scientific = FALSE))
```

### EXERCISE

Compute the mean and median return

### SUMMARIZE BY GROUP

```{r}
df %>% 
  filter(!is.na(return)) %>% 
  group_by(genre) %>% 
  summarise(mean_return = mean(return, na.rm = TRUE),
            median_return = median(return, na.rm = TRUE))
```

# VISUALIZATION

Visualizing distributions:

e.g. histograms for continuous variables
e.g. barplots for discrete variables

## HISTOGRAMS

Compute distribution of the production budget

```{r}
ggplot(df, aes(x = production_budget)) +
  geom_histogram(color = "black", fill = "gray", bins = 100)+
  theme_classic()
```

### Exercise

Visualize the distribution of box office returns per Dollar invested

## BARPLOTS

Success by Genre

1. Absolute

```{r}
df %>% 
  filter(!is.na(success)) %>% 
  ggplot(aes(x = genre, fill = success)) +
  geom_bar() +
  theme_classic()
```

2. Proportional

```{r}
df %>% 
  filter(!is.na(success)) %>% 
  ggplot(aes(x = genre, fill = success)) +
  geom_bar(position = "fill") +
  theme_classic()
```

### EXERCISE

Filter out all rows that have NA for 'success' and/or 'mpaa_rating'. Then compute the absolute and proportional movie success by mpaa_rating.

1. Absolute

2. Proportional
