---
title: "Effect Sizes & Meta-Analysis"
output: html_document
---

```{r setup, include=FALSE}
library(effsize)
library(effectsize)
library(metafor)
library(tidyverse)

Sys.setenv(LANG = "en")
```

# Effect Sizes 

Although effect sizes are an important value to report, they are not typically displayed in a standard output, for example from a t-test.


#Example data set for t-test
```{r}
set.seed(5)
data <- tibble(
  dv = c(rnorm(n = 10000, mean = 100, sd = 10),
         rnorm(n = 10000, mean = 99, sd = 10)),
  id = c(rep("a", 10000), rep("b", 10000))
  )

```

#Run a t-test on the variable "dv" by "id"
```{r}

```

What do the results of this t-test tell us?


How big is the difference actually between these two groups? Let's just look at the unstandardized means for each group:

```{r}

```


This doesn't seem like that big of a difference, but for a closer look, we can use effect size of standardized mean difference. That's where Cohen's d comes in. We can calculate this using the "effsize" package.
```{r}

```

Even though we found a significant effect, it was actually quite small.

There are a lot of packages that contain fucntions to calculate Cohen's d, with similar notation:

"lsr"
"effectsize"
"psych"

```{r}

```

# EXERCISE

Data frame with student grades and whether they had teacher A or teacher B
```{r}
grade <- c(55, 65, 65, 68, 70, 56, 60, 62, 66) #student grades
teacher <- c("A", "A", "A", "A", "A", "B", "B", "B", "B") #teacher 

exams <- data.frame(grade, teacher)
```

Compute the effect size for student grades by teacher. (Remember to think about the sample size and what this means about how we compute the effect size!)
```{r}

```

############################################

#Effect Sizes in Meta-Analysis

When conducting a meta-analysis, we often need to compute the effect sizes of interest for many studies. Doing this one by one would be super tedious, luckily we can use R and the package metafor to do it all in one go. 

## Standardized Mean Differences
```{r}
smd_meta<-data.frame(
  id = c("001","002","003","004","005","006","007","008","009","010","011"),
  author_year = c("Ruva 2007","Smith 2007","Chrzanowski 2006","Studebaker 2000",
                  "Hayes 2008","Bradshaw 2007","Longe 2010","Wilson 1998",
                  "Otto 1994","Locatelli 2011","Ramos 2005"),
  n1 = c(138,140,144,21,54,78,92,31,29,90,181),
  n2 = c(138,142,234,21,52,20,18,15,13,29,53),
  m1 = c(5.29,5.05,1.97,5.95,5.07,6.22,5.47,6.13,5.69,4.81,4.83),
  m2 = c(4.08,3.89,2.45,3.67,3.96,5.75,4.89,3.80,3.61,4.61,4.51),
  sd1 = c(1.65,1.50,1.08,1.02,1.65,2.53,2.31,2.51,2.51,1.20,1.19),
  sd2 = c(1.67,1.61,1.22,1.20,1.76,2.17,2.59,2.68,2.78,1.39,1.34)
)
```

# Calculating standardized mean differences for each study
```{r}

```

#Visualize the effect sizes using a forest plot
```{r}

```

#EXERCISE

Dataset with results from 9 studies on the length of hospital stay of stroke patients under specialized vs. non specialized care
```{r}
dat <- dat.normand1999
```

Calculate the SMDs for all the studies in the dataset
```{r}

```

Create a forest plot displaying the effect sizes and their confidence intervals
```{r}

```

## Correlation Coefficients

```{r}
cor_meta <- dat.mcdaniel1994
```

Use the escalc function to calculate the z-transformed correlations for all studies
```{r}

```
