---
title: 'Session 6: Advanced Data Wrangling'
author: "Niklas Cypris"
date: "25 5 2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(sjPlot)

get_mode <- function(x, na.rm = FALSE) { # from: https://stackoverflow.com/questions/2547402/how-to-find-the-statistical-mode
  if(na.rm){
    x = x[!is.na(x)]
  }

  ux <- unique(x)
  return(ux[which.max(tabulate(match(x, ux)))])
}
```

```{r load and prepare data}
load("./data/lm.Rda")
bechdel <- read_csv(file = "./data/bechdel.csv")
movies <- read_csv("./data/movies.csv")

movies <- movies %>% 
  filter(mpaa_rating %in% c("R", "PG-13")) %>% 
  mutate(returns = rowSums(select(., ends_with("_gross"))),
         budget_c = scale(production_budget, scale = FALSE)[,1],
         year_c = scale(release_date, scale = FALSE)[,1])
```

# VISUALIZING TRIPLE INTERACTIONS

https://strengejacke.github.io/sjPlot/articles/plot_interactions.html

```{r}
summary(lm2)
```

`terms`: Up to three predictors. Second and third predictor for grouping.

Grouping by interval scaled predictors: Usually at -1 SD, Mean, + 1 SD

## EXERCISE

```{r}
lm <- lm(returns ~ budget_c * year_c * mpaa_rating, movies)

summary(lm)
```

Visualize how the relationship between movie budget and returns varies based on mpaaa rating and release year.

```{r}

```

# JOINING DATA SETS

https://github.com/gadenbuie/tidyexplain

```{r make example data sets}
bechdel <- bechdel %>% 
  mutate(id = 1:nrow(.)) %>% 
  select(id, everything())

bechdel1 <- bechdel[1:(nrow(bechdel)-4),1:4]
bechdel2 <- bechdel[5:nrow(bechdel),c(1, 5:ncol(bechdel))]
```

## INNER JOIN

All rows from x where there are matching values in y, and all columns from x and y.

## LEFT JOIN

All rows from x, and all columns from x and y. Rows in x with no match in y will have NA values in the new columns.

## RIGHT JOIN

All rows from y, and all columns from x and y. Rows in y with no match in x will have NA values in the new columns.

## FULL JOIN

All rows and all columns from both x and y. Where there are not matching values, returns NA for the one missing.

## SEMI JOIN

All rows from x where there are matching values in y, keeping just columns from x.

## ANTI JOIN

All rows from x where there are not matching values in y, keeping just columns from x.

## EXERCISE

```{r make example data sets}
movies <- movies %>% 
  mutate(id = 1:nrow(.)) %>% 
  select(id, everything())

movies1 <- movies[1:(nrow(movies)-400), 1:3]
movies2 <- movies[200:nrow(movies), c(1, 4:ncol(movies))]
```

You want to join movies1 and movies2 to create a movies_new1 data frame. That data frame should contain all rows and columns from movies1 and all columns from movies2. Select the correct *join() command.

```{r}

```

You want to join movies1 and movies2 to create a movies_new2 data frame. That data frame should contain all rows and columns from movies1 and all rows and columns from movies2. Select the correct *join() command.

```{r}

```


# STRING MANIPULATIONS

## Separating text into different columns

separate(

`column to be split`,
`into =` list of new column names,
`sep =` separator

)

## EXERCISE

Split the `writer` column like the `director` column was split. How many columns do you need to create in order to discard additional pieces in less than 10 rows?


## Joining text columns into one

unite(

`col =` name of new column
`select` select columns to unite
`sep =`choose separator

)

## Selecting rows based on text


## EXERCISE

Choose your favorite director and see how many of their movies are included in this data set.

```{r}

```

## Extracting words from strings

https://github.com/rstudio/cheatsheets/blob/master/strings.pdf

## EXERCISE

Go on https://stackoverflow.com/questions/40113963/how-to-extract-everything-until-first-occurrence-of-pattern and figure out how to extract the first name of director_1.

```{r}

```


# APPLYING FUNCTIONS ACROSS MULTIPLE COLUMNS

Mean of all variables that measure movie returns


Grouped means

Centering all interval-scaled variables

## EXERCISES

Compute the mean for all uncentered interval-scaled variables 

```{r}

```

Compute the mode for all factor variables (get_mode).

```{r}

```

